The Multi-Stencil Framework: A Component-Based Approach to Orchestrate Stencils

### 2017-03-06 ARTICLES/IJPP/articleR1/introduction.tex
petites corrections

%JB: pourquoi tu parles de taches ?
One possible runtime execution model for HPC is based on dynamic scheduling of task graphs combined with message passing~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359}.
These models increase code portability and enable users to reach interesting performance on heterogeneous architectures.
%JB: j'enleverais ce qui est au dessus et je commencerait tout de suite avec "OpenMP c'est compliqué"
General purpose parallel languages, such as OpenMP~\cite{660313} and OpenCL~\cite{Stone:2010:OPP:622179.1803953} start to include these concepts.
For non-expert users however, these languages are difficult to use and make it complex to tune applications for a given architecture. 
An interesting approach that combines simplicity of use due to a high abstraction level with efficient execution consists in domain specific languages (DSL) and domain specific frameworks (DSF).
These solutions are specific to a given domain and propose a grammar or an API which is easy to understand for specialists of this domain.
Moreover, knowledge about the targeted domain can be embedded in the compiler that can thus automatically apply parallelization and optimizations techniques to produce high performance code.
Domain specific solutions are therefore able to separate end-user concerns from HPC concerns which is a requirement to make HPC accessible to a wider audience.

Many domain specific languages and frameworks have been proposed that claim to handle distinct specific use-cases each.
Each solution is however typically re-implemented from scratch.
In this paper, we claim that the sharing of common building blocks when designing DSLs or DSFs would increases re-use, flexibility and maintainability in their implementation.
%JB: J'ajoute cet argument, tu peux le retirer si tu trouves ça dangereux
It would also ease the creation of approaches and applications combining multiple DSLs and DSFs.

>>>>

\JB{pourquoi tu parles de taches ?}
One possible runtime execution model for HPC is based on dynamic scheduling of task graphs combined with message passing~\cite{Gautier:2013:XRS:2510661.2511383,Augonnet2011,wu:hal-01078359}.
These models increase code portability and enable users to reach interesting performance on heterogeneous architectures.
\JB{j'enleverais ce qui est au dessus et je commencerait tout de suite avec "OpenMP c'est compliqué"}
General purpose parallel languages, such as OpenMP~\cite{660313} and OpenCL~\cite{Stone:2010:OPP:622179.1803953} start to include these concepts.
For non-expert users however, these languages are difficult to use and make it complex to tune applications for a given architecture. 
An interesting approach that combines simplicity of use due to a high abstraction level with efficient execution consists in domain specific languages (DSL) and domain specific frameworks (DSF).
These solutions are specific to a given domain and propose a grammar or an API which is easy to understand for specialists of this domain.
Moreover, knowledge about the targeted domain can be embedded in the compiler that can thus automatically apply parallelization and optimizations techniques to produce high performance code.
Domain specific solutions are therefore able to separate end-user concerns from HPC concerns which is a requirement to make HPC accessible to a wider audience.

Many domain specific languages and frameworks have been proposed that claim to handle distinct specific use-cases each.
Each solution is however typically re-implemented from scratch.
In this paper, we claim that the sharing of common building blocks when designing DSLs or DSFs would increases re-use, flexibility and maintainability in their implementation.
\JB{J'ajoute cet argument, tu peux le retirer si tu trouves ça dangereux}
It would also ease the creation of approaches and applications combining multiple DSLs and DSFs.
